Species motif participation provides unique information about species risk of extinction

### 2022-06-07 manuscript/reorder_main_text.tex
minor

\author{Anna \r{A}kesson$^{1*}$, Alyssa R. Cirtwill$^{2*\dagger}$, Kate L. Wootton$^{3}$, Anna Ekl\"{o}f$^{1}$} 
\date{\small$^1$Department of Theoretical Biology, Chemistry, and Physics\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\
\medskip
\small$^2$Department of Agricultural Sciences\\
University of Helsinki\\
Helsinki, Finland\\
\medskip
\small$^3$ BioFrontiers Institute\\
University of Colorado, Boulder\\
U.S.A.
\medskip
* Joint first authors
\medskip
$^\dagger$ Corresponding author:\\

}

@@

    % Degree and TL don't explain everything
    The relationships between persistence and participation in the apparent competition and three-species chain motifs likewise demonstrate the potential for motif participation to synthesize different aspects of network structure.
    In these cases, in-degree and trophic level are not sufficient to explain the trends we observe in the motifs.
    Participation in the apparent competition motif was strongly negatively correlated with in-degree and shows a similar relationship to persistence.
    However, participation in the apparent competition motif was also strongly and positively correlated with trophic level, and the negative effect of high trophic levels on persistence is not reflected in the relationship between persistence and participation in the apparent competition motif.

>>>>

\author{Anna \r{A}kesson$^{1*}$, Alyssa R. Cirtwill$^{2*\dagger}$, Kate L. Wootton$^{3}$, Anna Ekl\"{o}f$^{1}$} 
\date{\small$^1$Department of Theoretical Biology, Chemistry, and Physics\\ 
Link\"{o}ping University\\
Link\"{o}ping, Sweden\\
\medskip
\small$^2$Department of Agricultural Sciences\\
University of Helsinki\\
Helsinki, Finland\\
\medskip
\small$^3$ BioFrontiers Institute\\
University of Colorado, Boulder\\
U.S.A.
\medskip
* Joint first authors
\medskip
$^\dagger$ Corresponding author\\
}

@@

    % Degree and TL don't explain everything
    The relationships between persistence and participation in the apparent competition and three-species chain motifs likewise demonstrate the potential for motif participation to synthesize different aspects of network structure.
    In these cases, in-degree and trophic level are not sufficient to explain the trends we observe in the motifs.
    For apparent competition, there were strong and opposing correlations with in-degree and trophic level but the relationship between apparent competition and persistence only matches the trends for in-degree.
    This suggests that some other factor is over-riding the relationship between apparent competition and trophic level.
